### 2019-08-19 maciek.tex
Lower bound, simplifications
Whiteboard pics

Consider clusters $A$ and $B$ that contain nodes $a_1, a_2, a_3$ and $b_1, b_2, b_3$, respectively.
The adversary begins with issuing three requests: $(a_1, a_2)$, $(b_1, b_2)$, and $(a_3, b_3)$.
Note that these require moving one of these pairs to a third cluster.
Our idea is that the OPT pays for the request $(a_3, b_3)$ only (i.e., it moves this pair to some cluster $C$), and all other requests are free for the OPT.

@@

At the begining, ALG has $\ell$ singleton-only components and each request increases their number by $1$.
Furthermore, before reaching either $d_1, d_2$ or $d_3$ in place of $x$ or $y$, the algorithm must cycle through $\Omega(\ell)$ nodes from other clusters. This is guaranteed as the choice of $D$ can depend on the actions of the deterministic algorithm.
In total, OPT pays $2$, and ALG pays $\Omega(\ell)$.

>>>>

Consider clusters $A$ and $B$ that contain nodes $a_1, a_2, a_3$ and $b_1, b_2, b_3$, respectively.
The adversary begins with issuing three requests: $(a_1, a_2)$, $(b_1, b_2)$, and $(a_3, b_3)$.
Note that these require moving one of these pairs to a third cluster.
Our idea is that the OPT pays for the request $(a_3, b_3)$ only (i.e., it moves this pair to a cluster $D$), and for OPT all other requests are free.

@@

At the begining, ALG has $\ell$ singleton-only components and each request increases their number by $1$.
Furthermore, before reaching either $d_1, d_2$ or $d_3$ in place of $x$ or $y$, the algorithm must cycle through $\Omega(\ell)$ nodes from other clusters. This is guaranteed as the choice of $D$ can depend on the actions of the deterministic algorithm.
In total, OPT pays $2$, and ALG pays $\Omega(\ell)$ (for each request besides the first two).
